MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-09-01 metaTracts-pvis2014.tex
no message

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers (CFRP) consist of two components: a matrix and a reinforcement. 
The base material for the matrix is typically a resin such as epoxy. 
The reinforcement provides the desired material characteristics. 
In case of CFRPs the reinforcements are typically bundles of individual carbon fibers (henceforth referred to as fiber bundle) woven into sheets of carbon fiber cloth which are layered and reinforced by an epoxy material. 
For quality control of CFRP materials and components industrial 3D X-ray computed tomography (XCT) is increasingly applied as it allows detailed characterizations of the material in a non-destructive manner.

This work contributes to the state of the art of CFRP characterization by the introduction of MetaTracts, a technique for extracting and visualizing fiber bundles and the geometric structure of the weaving pattern in fiber reinforced composites scanned with X-ray computed tomography. 
The declared goal of this work is to analyzing large areas of CFRPs using XCT scans of low resolution, in which individual fibers are barely visible. 
To reach this goal we apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. 
In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
Next, the extracted fiber bundle sections are clustered using a two step approach, wherein we first cluster according to orientation and then  cluster by proximity. 
We evaluate our algorithm on a number of data sets and demonstrate that MetaTracts effectively and robustly identifies and separates different fiber bundles. 
%mention user study here?%
This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract

>>>>

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers (CFRP) typically consist of two main components: the matrix and the reinforcement. 
Most important in order to achieve the desired characteristics of a CFRP is the reinforcement component. 
In case of CFRPs the reinforcements typically consist of bundles of endless carbon fibers woven into sheets of carbon fiber cloth, which are then layered and combined to a CFRP by the matrix component. 
For quality control of CFRP materials and components industrial 3D X-ray computed tomography (XCT) is increasingly applied as it allows detailed characterizations of the material in a non-destructive manner.

The presented work contributes to the state of the art of CFRP characterization by the introduction of MetaTracts, a technique for extracting and visualizing fiber bundles and the geometric structure of the weaving pattern in fiber reinforced composites scanned with X-ray computed tomography. 
The declared goal of this work is to analyze large areas of CFRPs using XCT scans of low resolution, in which individual fibers are barely visible. 
To reach this goal we apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. 
In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
Next, the extracted fiber bundle sections are clustered using a two step approach, wherein we first cluster according to orientation and then  cluster by proximity. 
We evaluate our algorithm on a number of datasets and demonstrate that MetaTracts effectively and robustly identifies and separates different fiber bundles. 
%mention user study here?%
This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract
